### 2023-03-20 Manuscript/Draft1.Rmd
add comments

@@

@@

@@

@@

@@

@@

@@

When combining population trends for each species, differing temperature scenarios, altering seasons, and sampling possibilities (noise, strata, covariates) there are a large number of scenario combinations to consider. The columns in Table \@ref(tab:scenarios) show the choices that define each scenario.

@@

[[We'll want to expand the results section to focus on the impact of each factor one at at time within each species. This will be a bit dull, but it is important to walk through the results in words to ensure that readers get the message. They can of course examine the tables in detail and draw their own conclusions, but we should put our interpretation down on paper.]]

@@

@@

#param_table1 = read_csv("CSVs/Cod_results.csv")
param_table1 = read_csv("CSVs/Cod_results_newsettings_forpaper.csv")

@@

#param_table1 = read_csv("CSVs/Cod_results.csv")
param_table1 = read_csv("CSVs/Haddock_results_newsettings_forpaper.csv")

>>>>

<!-- Paragraph above: Stocks in this region are not managed by NEFSC, they are assessed by us. The management is done by the Councils and GARFO. NEFSC actually only assesses the federally managed stocks (not the state managed stocks like tautog). We also assess some of the invertebrate stocks, such as squid, scallops, ocean quahogs, etc., in addition to fish stocks. Perhaps easier to focus on the bottom trawl itself and replace the first two sentences with something like The NEFSC has conducted a bottom trawl survey since 1963 to support assessment and management of the fish and invertebrate populations in the region (azaorivitz and politis refs).  -->

@@

<!-- Agree that could bulk up the above paragraph with references from the initial proposal, along with more recent refs like https://doi.org/10.1016/j.fishres.2023.106652, DOI 10.1007/s11160-016-9444-z, https://doi.org/10.1093/icesjms/fsac140, etc. Don't want to lose connection with the next paragraph, so don't get lost in the weeds. -->

@@

<!-- General note: we should do a sweep through entire document and change everything to past tense. This is the typical verb tense in fisheries papers (I know present tense is used in other fields). In above paragraph, need to add VAST and VAST with covariates. -->

@@

<!-- In the second sentence above, can we give a general size of the space occupied by each cell in our study? I know it varies by latitude, but I think an approximate size would be useful for readers to demonstrate that we are dealing with relatively small scale phenomena in the simulations. I stumbled over inhabit, inhabit, exist in the final sentence. I don't have a good suggestion for fixing it, just noting that the different final term caught my eye and made me ask if yellowtail were different from cod and haddock somehow. -->

@@

<!-- I think we can delete the sentence about using Beverton-Holt recruitment because it appear in the table.  -->

@@

<!-- I don't think this paragraph accurately represents what we did because we did the full factorial for yellowtail, but only some for cod and haddock. Need to think about how to restructure this paragraph to better reflect what we did. -->

@@

<!-- Can we simplify the third and fourth sentences to say something like "Randomly selected cells were sampled each year."? I realize the current text is more accurate, but worry that we may be losing the readers in the details. -->

@@

<!-- Note the Table XXX needs to be added comment above. -->
When combining population trends for each species, differing temperature scenarios, altering seasons, and sampling possibilities (noise, strata, covariates) there are a large number of scenario combinations to consider. The columns in Table \@ref(tab:scenarios) show the choices that define each scenario.

@@

<!-- [[We'll want to expand the results section to focus on the impact of each factor one at at time within each species. This will be a bit dull, but it is important to walk through the results in words to ensure that readers get the message. They can of course examine the tables in detail and draw their own conclusions, but we should put our interpretation down on paper.]] I think the above paragraphs are addressing this comment, but wanted to be sure they are not just "notes to self" before providing comments on them. -->

@@

<!-- Funding source is "Northeast Fisheries and Climate program at the NEFSC" -->

@@

#param_table1 = read_csv("CSVs/Cod_results.csv")
param_table1 = read_csv("CSVs/Cod_results_newsettings_forpaper.csv") # not in repo

@@

#param_table1 = read_csv("CSVs/Haddock_results.csv")
param_table1 = read_csv("CSVs/Haddock_results_newsettings_forpaper.csv") # not in repo
